---
title: "Dashboard"
author: "Ope"
date: "7/7/2021"
output: html_document
---
#step 1, Install library
#step 2, start importing the library below


```{r}
getwd()
```

```{r}
library(flexdashboard)
library(ggplot2)
library(readr)
library(highcharter)
library(dplyr)
library(tidyverse)
```



#step 3, load the data set into r
```{r}
train <- read_csv('train.csv')
head(train) #check the first six row
```
# Next function i wntb to use is str()
i wanna check what databtype are the column
```{r}
str(train)#It is to check the data type
```
# Next tell r to cast the column called pclass as a factor(like a category class)




```{r}
train$Embarked <- factor(train$Embarked, labels = c("Cherbourg", "Queenstown", "Southampton"))
str(train)
```



```{r}
head(train)
```



#let check how many row we have on the data
```{r}
nrow(train)
ncol(train)
```



```{r}
data.frame(train)
```




```{r}
str(train)
```


```{r}
sum(train$Pclass == "1st")
```


```{r}
trainn<-unlist(lapply(train, is.numeric))
trainn
```


```{r}
starwarss <- unlist(lapply(starwars, is.numeric))
starwarss
```

```{r}
head(starwars)
```


```{r}
colSums(is.na(train))
```




```{r}
head(train)
```

#A value box display a value (usually a number) in large text, with a smaller caption beaneath, and a large icon on the right side
#this is the syntax for creating valuebox and case sensitive https://pkgs.rstudio.com
#valueBox(value, caption = Null, icon = Null, color = Null, href = Null)
```{r}
valueBox(2222, icon = "fa-ship", color="rgb(100,100,100)")
```
##valuebox for percentage of survivors
```{r}
valueBox("31.6%", icon = "fa-heart", color = "200,100,100")
```
# To filter male
```{r}
tmp_males = train %>% filter(Sex =="male", !is.na(Age))
tmp_males
```


```{r}
unique(tmp_males$Sex)
```



```{r}
rep(x, times=3) # Apply rep with each argument 

```



```{r}
nrow(tmp_males)
```


```{r}
rep(x, len = 7)
```


#lets filter the female passenger by their Age and put them in a frame
```{r}
df <- data.frame(Age=c(as.mid,b$mids),Density=c(a.density,b$density),Sex=c(rep("female",length(as.mids)),rep("male",length(as.mids))))
df
```



```{r}
tmp_male <- train %>%  filter(Sex=="male", !is.na(Age)) %>% select(Age) %>% .[[1]]

b <- hist(tmp_male, 20, plot=TRUE)

tmp_male
```


```{r}
tmp_female <- train %>%  filter(Sex=="female", !is.na(Age)) %>% select(Age) %>% .[[1]]

a <- hist(tmp_female, 20, plot = TRUE)

tmp_female
```




```{r}
df <- data.frame(Age=c(a$mids,b$mids),Density=c(a$density,b$density),Sex=c(rep("female",length(a$mids)),rep("male",length(b$mids))))

df
```




```{r}
Age = data.frame(train$Age)
```







```{r}
tmp_male <- train %>%  filter(Sex=="male", !is.na(Age)) %>% select(Age) %>% .[[1]]

b <- hist(tmp_male, 20, plot=FALSE)

#filter out female
tmp_female <- train %>%  filter(Sex=="female", !is.na(Age)) %>% select(Age) %>% .[[1]]

a <- hist(tmp_female, breaks = b$breaks, plot=FALSE)

df <- data.frame(Age=c(a$mids,b$mids),Density=c(a$density,b$density),Sex=c(rep("female",length(a$mids)),rep("male",length(b$mids))))

highchart() %>% 
  hc_add_series(name="female", select(filter(df,Sex=="female"),Density)[[1]], type="column", color='rgba(255, 192, 203, 0.30)', showInLegend=FALSE) %>% 
  hc_add_series(name="male", select(filter(df,Sex=="male"),Density)[[1]], type="column", color='rgba(68, 170, 255, 0.30)', showInLegend=FALSE) %>% 
  hc_add_series(name="male", select(filter(df,Sex=="male"),Density)[[1]], type="spline", color="#44AAFF") %>% 
  hc_add_series(name="female", select(filter(df,Sex=="female"),Density)[[1]], type="spline", color="#FFC0Cb") %>% 
hc_tooltip(pointFormat = "<span style=\"color:{series.color}\">{series.name}</span>:
             {point.y:.3f}<br/>",
             shared = FALSE) %>% 
  hc_yAxis(title=list(text='Density')) %>% 
  hc_xAxis(title=list(text='Age'))   
```






```{r}
tmp <- train %>% filter(!(Embarked=="")) %>% group_by(Embarked) %>% tally() %>% mutate(Percent = n/sum(n))
tmp$colors <- c("#d35400", "#2980b9", "#2ecc71")
tmp <- arrange(tmp,desc(Percent))
highchart() %>% 
  hc_xAxis(categories = c("Southhampton", "Cherbourg", "Queenstown")) %>%
  hc_yAxis(title=list(text='Percentage')) %>%
  hc_add_series(tmp, "bar", hcaes(x = Embarked, y = Percent, color=colors)) %>% 
  hc_tooltip(pointFormat = "{point.y:.2f}</br>",shared = FALSE) %>% 
  hc_legend(enabled=FALSE)
```



```{r}
tmp <- train %>% group_by(Pclass) %>% summarise(Survived = mean(Survived))
tmp$colors <- c("#d35400", "#2980b9", "#2ecc71")
hchart(tmp, "column", hcaes(x = Pclass, Y = Survived, color = colors)) %>%
  hc_tooltip(pointFormat =  "{point.y:.2f}</br>",shared = FALSE)
```


```{r}
tmp <- train %>%  group_by(Pclass) %>% summarize(Survived = mean(Survived))
tmp$colors <- c("#d35400", "#2980b9", "#2ecc71")
hchart(tmp, "column", hcaes(x = Pclass, y = Survived, color=colors)) %>% 
    hc_tooltip(pointFormat = "{point.y:.2f}</br>",shared = FALSE)
```




```{r}
rate <- 10
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(success = c(80, 100), warning = c(40, 79), danger = c(0,39)))
```



```{r}
rate <- 95
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```
