---
title: "Football Analysis"
author: "Ope"
date: "8/24/2021"
output: html_document
---
#The note is a submission on a task for the most expensive football transfer

```{r}
library(tidyverse)
library(janitor)
library(ggthemes)
library(hrbrthemes)
library(RColorBrewer)
```
#Reading and viewing the dataset

```{r}
data <- read.csv("football_players.csv")
head(data)
```
#Filtering the data and rename

```{r}
data2 <- data %>% 
  select(Rank, Player, From.Club., To.Club.,Origin, Position, Fee.â...mln., Year) %>% 

  rename("From_Club"= "From.Club.", "To_Club" = "To.Club.","Fee_Euro_mln" = "Fee.â...mln.")


head(data2)
```
#Number of clubs with atleast one expensive  transfer

```{r}
club_d <- n_distinct(data2$`To_Club`)
club_d

#SIXTEEN CLUBS have bought a player for a record fee during the time period 2000 -2021
```




```{r}
view(data2)
```

   #Names of the club with atleast one expensive transfer
   
```{r}
club_names <- data.frame( unique(data2$`To_Club`)) %>% 
  rename("Club with atleast one expensive player" = "unique.data2.To_Club.")
club_names
```
#Identifying the transfer time period

```{r}
data3 <- data2 %>% 
  
   summarise(Min_yr= min(Year), Max_yr = max(Year))
data3
 #Data shows that recordfee took place with the span of 2000 to 2021
```
   #Clubs And There Total Spending Between 2000 - 2021_Spending_in_Euro_mln
```{r}
club_tot <- data2 %>% 
 
  group_by(To_Club)%>% 
  summarise( Total_Spending = sum(Fee_Euro_mln)) %>%
  arrange(desc(Total_Spending))
  
club_tot
```


```{r}
names(data2)
```
```{r}
nb.cols <- 16
mycolors <- colorRampPalette(brewer.pal (8,"Pastel1"))(nb.cols)
nb.cols
mycolors 
```
  

```{r}


ggplot(club_tot,aes(reorder(To_Club,Total_Spending)))+
  geom_col(aes(x=reorder(To_Club,Total_Spending) ,y=Total_Spending ,fill=To_Club))+
  coord_flip()+
  theme_economist()+
  #scale_fill_manual(values = mycolors )+
  #theme(plot.title = element_text("Total Club Spending From 2000-2021"))+ap
  labs(title = "Total Club Spending On Record Fee Transfer From 2000-2021",
       x = "Clubs",
      y = "Total Spending In Euro Million",
      caption = "Data From Kaggle Analysed By Fahd Using r (Data Science)")+
  theme(axis.text.x = element_text( hjust = 1, size =8, angle = 90),
       axis.title.x = element_text(size = 23),
        axis.title.y = element_text(size = 16),
        plot.title = element_text(hjust = 1), 
       legend.position = "none",
       plot.caption = element_text(size = 11,  hjust = 1))+ 
  geom_label( aes(To_Club, Total_Spending,label= Total_Spending)) 
  

  #data = club_tot, aes(To_Club,Total_Spending,fill = "green")

  #Barcelona has spend more money than other clubs in the transfer  market during the 2000-2021. Their total amount is 656.8(min)
```
#Top 10 most expensive player from 2000-2021

```{r}
view(data2)

```





```{r}
top_player <- data2 %>%
  select(Player,Year, Fee_Euro_mln)%>%
  arrange(desc(Fee_Euro_mln))
top_player


```

```{r}
data2
```


```{r}
Top_player <-top_player[1:10,] %>% 
  ggplot(aes(Player,Fee_Euro_mln))+
  geom_col(aes(reorder(x =Player,Fee_Euro_mln ), y = Fee_Euro_mln, fill=Player))+
  coord_flip()+
  theme_economist()+
  labs(title = "Top 10 Most Expensive Players In 2000-2021", caption = "Data From Kaggle Analysed by Ope using r (Data Science)",
       x = "Players",
       y = "Fee_Mln_Euro")+
  theme(plot.title = element_text(hjust = 0.5),
          legend.position = "none",
        axis.title.y = element_text(size = 18, color =  "Blue"),
        axis.title.x = element_text(size = 18, color =  "Blue"),
        plot.caption = element_text(size = 13, hjust = 1))+
  geom_label(aes(Player,Fee_Euro_mln, label= Year))
  

 Top_player 

#This are the 10 most expensive transaction made on a player from 2000-2021

```



```{r}
Top_player
```
#Barcelona most expensive players 2000 - 2021
  
```{r}
bar_players <- data2 %>%
  select(Player, To_Club,Fee_Euro_mln, Position,Year ) %>% 
  filter(To_Club == "Barcelona" ) %>% 
  arrange(desc(Fee_Euro_mln)) %>%
  
  ggplot(aes(Player,Fee_Euro_mln))+
  geom_col(aes(reorder(x =Player, Fee_Euro_mln), y= Fee_Euro_mln,fill= Position))+
  theme_economist()+
  labs(title = "Barcelona Most Expensive player 2000 - 2021", 
       caption = "Data From Kaggle Analysed By Fahd Using r (Data Science)",
       x = "Players",
       y = "Fee_Mln_Euro")+
  theme(plot.title =element_text(size = 21, hjust = 1.2),
        axis.title.x = element_text(size = 18, color="green" ),
        axis.title.y = element_text(size = 18, color = "green"),
        plot.caption = element_text(size = 13, hjust =1))+
        #legend.position  = "none")+
        #axis.text.x = element_text(angle = 90, size= 10))+
  coord_flip()+
  geom_label(aes(Player,Fee_Euro_mln,label =Year ))
  
bar_players 

# Data Shows 10 Most Expensive Signed Players From 2000_2021 In Barcelona Team


```


```{r}
 real_Total <- data2 %>%
  select(Player, To_Club, Fee_Euro_mln, Position,Year)%>%
  filter( To_Club =="Real Madrid") %>%
  arrange(desc(Fee_Euro_mln)) %>%
  
  ggplot(aes(Player, Fee_Euro_mln))+
  geom_col(aes(reorder(Player,Fee_Euro_mln), y = Fee_Euro_mln, fill = Position))+
   theme_economist()+
  labs(title = "Real Madrid Most Expensive player 2000 - 2021", 
       caption = "Data From Kaggle Analysed By Fahd Using r (Data Science)",
       x = "Players",
       y = "Fee_Mln_Euro")+
  theme(plot.title =element_text(size = 21, hjust = 1.2),
        axis.title.x = element_text(size = 21, color="Grey" ),
        axis.title.y = element_text(size = 21, color = "Grey"),
        plot.caption = element_text(size = 13, hjust =1))+ 
        #legend.position  = "none")+
        #axis.text.x = element_text(angle = 90, size= 10))+
  coord_flip()+
  geom_label(aes(Player,Fee_Euro_mln,label =Year ))
  
    #Data Shows 10 Most expensive signing in Real Madrid  Gareth Bale Make the all time record 2000-2021
real_Total
```

```{r}

mancity_Total <- data2 %>%
  select(Player,To_Club,Position, Fee_Euro_mln,Year) %>%
  filter(To_Club == "Manchester City") %>%
  arrange(desc(Fee_Euro_mln)) %>%
  
  ggplot(aes(Player,Fee_Euro_mln))+
  geom_col(aes(reorder(x=Player, Fee_Euro_mln), y =  Fee_Euro_mln, fill = Position))+
   theme_economist()+
  labs(title = "Manchester City Most Expensive player 2000 - 2021", 
       caption = "Data From Kaggle Analysed By Fahd Using r (Data Science)",
       x = "Players",
       y = "Fee_Mln_Euro")+
  theme(plot.title =element_text(size = 21, hjust = 0.9),
        axis.title.x = element_text(size = 21, color="Red" ),
        axis.title.y = element_text(size = 21, color = "Red"),
        plot.caption = element_text(size = 13, hjust =1))+ 
        #legend.position  = "none")+
        #axis.text.x = element_text(angle = 90, size= 10))+
  coord_flip()+
  geom_label(aes(Player,Fee_Euro_mln,label =Year ))
  
 #Data Shows 10 Most Expensive Signing In Manchester City, Jack Grealish Making the all time record
mancity_Total
```


```{r}
psg_Total <- data2 %>% 
  
  select(Player, To_Club, Position, Fee_Euro_mln, Year)%>%
  filter(To_Club == "Paris Saint-Germain") %>%
  
  ggplot(aes(Player,Fee_Euro_mln ))+
  geom_col(aes(reorder(x =Player, -Fee_Euro_mln),y = Fee_Euro_mln, fill =Position ))+
  theme_economist()+
  labs(title = "Paris Saint-Germain  Most Expensive player 2000 - 2021", 
       caption = "Data From Kaggle Analysed By Ope Using r (Data Science)",
       x = "Players",
       y = "Fee_Mln_Euro")+
  theme(plot.title =element_text(size = 18, hjust = 0.9),
        axis.title.x = element_text(size = 21, color="brown" ),
        axis.title.y = element_text(size = 21, color = "brown"),
        plot.caption = element_text(size = 13, hjust =1))+
       # legend.position  =  )+
        #axis.text.x = element_text(angle = 90, size= 10))+
  #coord_flip()+
  geom_label(aes(Player,Fee_Euro_mln,label =Year ))
  
  


psg_Total
```
```{r}
data2
```


```{r}

Arsen_Total <- data2 %>% 
  select(Player, To_Club, Position, Fee_Euro_mln, Year) %>% 
  filter(To_Club == "Arsenal") %>% 
  
  ggplot(aes(Player, Fee_Euro_mln))+
  geom_col(aes(fill =  Position))+
   theme_economist()+
  labs(title = "Arsenal Most Expensive player 2000 - 2021", 
       caption = "Data From Kaggle Analysed By Ope Using r (Data Science)",
       x = "Players",
       y = "Fee_Mln_Euro")+
  theme(plot.title =element_text(size = 21, hjust = 0.9),
        axis.title.x = element_text(size = 21, color="purple" ),
        axis.title.y = element_text(size = 21, color = "purple"),
        plot.caption = element_text(size = 13, hjust =1))+ 
        #legend.position  = "none")+
        #axis.text.x = element_text(angle = 90, size= 10))+
 # coord_flip()
  geom_label(aes(Player,Fee_Euro_mln,label =  Year))

Arsen_Total 

```


```{r}
Countries_Data <- data2%>%
  mutate(Countries =Origin ,
           Countries = recode(Countries, Wakes = "Wales" )) %>%
  select(Countries, Origin, Fee_Euro_mln) %>%
  group_by(Countries) %>% 
  summarise(Origin = n(), Total = sum(Fee_Euro_mln)) %>% 
  arrange(desc(Total)) %>%
  
  ggplot(aes(Countries,  Total))+
  geom_col(aes(reorder(x = Countries, Total), y = Total, fill =Countries ))+
  theme_bw()+
  labs(title = "List Of Club Record Fee Transfer By Origin Country 2000 - 2021", 
       subtitle = "French player are the most demanded",
       caption = "Data From Kaggle Analysed By Ope Using r (Data Science)",
       x = "Countries",
       y = "Fee_Mln_Euro")+
  theme(plot.title =element_text(size = 16, hjust = 1.1),
        axis.title.x = element_text(size = 21, color="Red" ),
        axis.title.y = element_text(size = 21, color = "Red"),
        plot.caption = element_text(size = 13, hjust =1),
        legend.position  = "none",
        axis.text.x = element_text(angle = 45, size= 10))+
  coord_flip()+
  geom_label(aes( Countries, Total,label =Origin ))
  
  
 Countries_Data
 
 #The French player are the most in demand in football sitting at the 1st Brazil is the second 
```
```{r}

 Trans_Year <- data2 %>% 
  mutate( "YEar" =Year ) %>% 
  select(YEar, Year, Fee_Euro_mln)%>%
  group_by(Year) %>% 
  summarise(YEar = n(), Total = sum(Fee_Euro_mln))%>%
  rename("Count"=YEar) %>% 
  arrange(desc(Total))


Trans_Year

#The Table Below Show The Data Of Transfer Count Year Bases... We Have Come To The End Of The Report.
```

