---
title: "Multiple Linear Regression"
author: "Ope"
date: "8/11/2021"
output: html_document
---



#supervised learn model with linear Regression

 -Baby Steps
 
 Collecting the Data
 Capturing the data in R
 Checking for linearity
 Applying the mutiple linear regression model
 making a prediction
 
 'step  1: Collect the data
 
 
 so lets with the simple exampke where the goal is to predict the stock index price (dependent Variable) of a ficitious economy based on two independent/input varibles;
 
      'Interest_Rate - Independent Variable
      'Unemployment_Rate - Independent Variable
      'Depended Variable - Stock price is what we wish to predict
      
      
  #Lets create a small data to use
  
```{r}
Year <- c(2017, 2017, 2017, 2017, 2017,2017,2017,2017,2017,2017,2017,2017,2016,2016,2016,2016,2016,2016,2016,2016,2016,2016,2016,2016)

length(Year)
```


  
```{r}
Month <- c(  12,11,10,9,8,7,6,5,4,3,2,1,12,11,10,9,8,7,6,5,4,3,2,1)
length(Month)
```
```{r}
Intrest_Rate <- c(2.75,2.5,2.5,2.5,2.5,2.5,2.5,2.25,2,25,2.25,2,2,2,1.75,1.75,1.75,1.75,1.75,1.75,1.75,1.75,1.75,1.75)

length(Intrest_Rate)
```
#Assuming there are monthly data for unemployment rate

```{r}
Unemployment_Rate <- c(5.3,5.3,5.3,5.3,5.4,5.6,5.5,5.5,5.5,5.6,5.7,5.9,6,5.9,5.8,6.1,6.2,6.1,6.1,6.1,5.9,6.2,6.2,6.1)

length(Unemployment_Rate)

```
#Lets assume these are our different stock price index data released by Jp Morgan Chase, its is one of the most large bank in US

```{r}
Stock_Idex_Price <- c(1464,1394,1357,1293,1256,1254,1234,1195,1159,1167,1130,1075,1047,965,943,958,971,949,884,866,876,822,704,719)

length(Stock_Idex_Price)
```
```{r}
getwd()
```
```{r}
df = do.call(rbind, Map(data.frame, Year=Year, Month=Month, Unemployment_Rate= Unemployment_Rate, Stock_Idex_Price = Stock_Idex_Price, Intrest_Rate = Intrest_Rate))

df
```
```{r}
str(df)
```
```{r}
dim(df)
```
```{r}
nrow(df['Stock_Idex_Price'])
```


            'Step 3; Let's check for linearity'
    Before you apply linear regression models, you'll need to verify that sevral assumption are met, Most notably you ll need to
    
    make sure that  linear relationship  exist between the dependent variable and the independent variable/s
    
    A quick way to check for linearity is by using scatter plots.
    
    For Our Example, we will need to check that a linear relationship exist between;
    
    The stock_Index_Price (dependent Variable) and the Intrest_rate (independent varoable ) and
    
    The Stock_Index_Price (dependent Variable) and the unemployment rate (independent Variable)
    
    
```{r}
max(df$Stock_Idex_Price)
min(df$Stock_Idex_Price)
```
```{r}
plot(x = Intrest_Rate, y = Stock_Idex_Price)
```
    
```{r}
library(ggplot2)

 linear  <- ggplot(df, aes(x = Intrest_Rate, y = Stock_Idex_Price))+
            geom_point(position = "jitter")
        
  linear      
```
```{r}
write.csv(df,"linear reg.csv")
```
    
    
```{r}
cor(Stock_Idex_Price,Intrest_Rate)
```
```{r}
cor(Stock_Idex_Price,Unemployment_Rate)
```
    'Note you will notice that indeed a linear relationship exists between the stock_Index_Price and the Intrest_Rate, specifically, when intrest rate goes up, the stock index goes up as well'
    
    
```{r}
plot(x=Unemployment_Rate, y = Stock_Idex_Price)
```
                    Apply  the multiple linear in R
                    
```{r}
#model = lm(Dependent Variable ~ First indepent variable + Second Independent model + ......)
#summary(madel)
```
                    
```{r}
model = lm(Stock_Idex_Price ~ Intrest_Rate + Unemployment_Rate)
summary(model)
```
    Y= M1X1 + M2X2 + ......C      
    
 'You can use the coefficient in the summary in order to build the multiple linear regression equation as follows:
 
 Stock_Index_Price = (Intercept) + (Intrest_Rate coef )*x2
 
 
 X1 means the unknown intrest rate
 x2 means unknown employment rate
 
 And Once you plug the number from the summarry;
 
 Stock_Index_Price = (1798.4) + (345.5)*X1 +  (-250.1)*X2`
 
 
         'Step 5 Make a Predection
         
Now let make a prediction based on equation above

For example, imagine that you want to predict the stock index price after  you collected the following data:



        Intrest Rate = 1.5 (i.e., X1 = 1.5)
        Unemployment Rate = 5.8(i.e., X2= 5.8)
        
And If You Plug that into regression equation you'll get:

stock_Index_Price = (1798.4) + (345.5)*(1.5) +(-250.1)*(5.8 )= 866.07

Y = c + m1x1 + m2x2

Y = m1x1 + m2x2 +m3x3 +......

```{r}
Stock_Idex_Price = (1798.4) +  (345.5)*(1.5) + (-250.1)*(5.8)
Stock_Idex_Price
```


The Predected stock value for the stock_Index_Price os therefore 886.07
    
    