---
title: "Travel_Insurance Dataset"
author: "Ope"
date: "8/20/2021"
output: html_document
---

   #Travel Insurance prediction Dataset
   
#Buisness task and stakeholders
. The buisness task for this case study is to see what factor correlates with purchasing travel insurance and how to overcome this obstacle.

.Stakeholders are airline x and the developers of the website to make the neccesary adjustments.


#Set goals and questions for the case study 

. Explore the dataset at hand
.see what factor stand out in why customers do/do not purchase Travel Insurance
.Set prediction using linear regression - TBD
.Suggest how to overcome low purchase of Travel insurance


#Data source usewd
Data content; This data set contains information about different factors that can contribute to the purchasing travel insurance. This include age, salary, the amount of family member and travel history

```{r}
library(tidyverse)
library(data.table)
library(ggplot2)
library(reprex)
```


```{r}
?reprex
```

```{r}
Travel_Insurance <- read.csv("TravelInsurancePrediction.csv")
```


#Preview data
Here, we preview the data in R to see what we are working with

```{r}
head(Travel_Insurance)
warning = FALSE
```
#Structure of my data
Here we look at the structure of the data by using the following code 

```{r}
str(Travel_Insurance)
```
```{r}
view(Travel_Insurance)
```

#Exploring the data_set

Age
Finding out the min and max of age's from the dataset and creating a graph showing AgeVpurchasing Travel Insurance

```{r}
AgeVInsurance <- Travel_Insurance %>%
  ggplot(aes(Age, TravelInsurance))+
  geom_bar(stat= "identity" , fill = "#85C1E9")+
  labs(title= "AGE v TRAVEL INSURANCE", caption = "Data From Kagglel")+
   theme(plot.title = element_text(hjust = 0),
         axis.title.x = element_text(size = 23, color = "Black"),
         axis.title.y = element_text(size = 23, color = "Green"),
         axis.text.x = element_text(size = 13,color =  "Black"),
         axis.text.y = element_text(size = 13, color = "Black"))

ggplotly(AgeVInsurance, tooltip = "y")

 
```


```{r}
AgenInsurance <- Travel_Insurance %>%
  ggplot( aes(Age, TravelInsurance))+
  geom_smooth(method = lm)+
  labs(title = "Age V Travel Insurance", caption = "Data Collected by kaggle",
       X = "Age",
       Y = "Travelinsurance ")+
theme(plot.title = element_text(hjust = 0.5, size = 23),  
      axis.title.x = element_text( size = 23, color = "Green"),
      axis.title.y = element_text( size =  23, color = "Black"),
      axis.text.x  = element_text(size = 10, color ="Black"),
      axis.text = element_text(size = 10, color = "Black"))
AgenInsurance
```


```{r}
unique(Travel_Insurance$TravelInsurance)
unique(Travel_Insurance$Age)
```
Employment Type
creating a graph showing Employment Type V Purchasing Travel Insurance


```{r}
 EmpnInsurance <- Travel_Insurance %>%
  ggplot(aes(Employment.Type,TravelInsurance))+
  geom_bar(stat = "identity", fill= "blue" )+
  labs( title ="Employment.TypevTravelInsurance", subtitle = "Employments", caption =  "Data From Kaggle By Fahd" )+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5, size = 22),
        axis.title.x = element_text(size = 19, colour = "Green"),
        axis.title.y = element_text(size = 19, color = "Black"),
        axis.text.x = element_text(size = 12, colour = "Black"),
        axis.text.y = element_text(size = 12, colour = "Black"),
        axis.text.x.top = element_text(size = 23,colour = "Blue"))
  
  
 ggploty( EmpnInsurance, tooltip = "y")


```
#Annual Income
Creating a graph showing Annual Income V Purchasing Travel Insurance

```{r}
Travel_Insurance %>%
  ggplot(aes(AnnualIncome,TravelInsurance))+
  geom_smooth(method = lm)+
  theme_classic()+
  labs(title = "Annualinc V TravelInsurance", subtitle = "Annual Income", caption = "Data from Kaggle by  Ope" )+
  theme(plot.title = element_text(hjust = 0.5, size = 20, colour = "Blue"),
        axis.title.x = element_text(size = 18,colour = "Black"),
        axis.title.y = element_text(size = 18, color = "Black"),
        axis.text.x = element_text(size = 18, colour = "Black"),
        axis.text.y = element_text(size = 18,colour = "Black"))


```


```{r}
names(Travel_Insurance)
```
#Creating a graph showing how many people have chronic disease

```{r}
HCDisease <- Travel_Insurance %>%
  ggplot(aes(ChronicDiseases))+
    geom_histogram(binwidth = 1, fill= "#24E4F6")+
  labs(title = "Histogram Of ChronicDisease", subtitle = "Disease", x = "Chronic Disease",
       y ="frequency")+
  theme_bw()+
  theme(plot.title = element_text(size = 23, hjust = 0.5 ),
        axis.title.x = element_text(size = 15, color = "Blue"),
        axis.title.y  = element_text(size = 15, color = "Black"),
        axis.text.x = element_text(size = 13, color =  "Black"),
        axis.text.y = element_text(size = 13, color = "Black"))
  
ggplotly(HCDisease, tooltip = "x")

```

```{r}
hist(Travel_Insurance$ChronicDiseases, breaks= 2, col = "#85C1E9")
```

#Creating a graph showing a frequent flying status v purchasing Travel Insurance

```{r}
freqflyer <- Travel_Insurance %>%
  ggplot(aes(FrequentFlyer, TravelInsurance))+
  geom_bar(stat = "Identity", fill= "#85C1E9")+
  labs(title = "Frequent Flyer V TravelInsurance", subtitle = "frequentflyer", x = "FREQUENTFLYER",
       y = "TRAVELINSURANCE")+
  theme_bw()+
  theme(plot.title = element_text(size = 23, colour = "black", hjust = 0.5),
        axis.title.x = element_text(size =  15),
          axis.title.y =  element_text(size = 15),
        axis.text.x = element_text(size = 13, colour = "black"),
        axis.text.y = element_text(size = 13, colour = "black"))

 ggplotly(freqflyer, tooltip = "y")
```

#Creating a graph showing travelling abroad V purchasimg travel insurance

```{r}
 Travel_Insurance %>%
  ggplot(aes(EverTravelledAbroad,TravelInsurance))+
  geom_bar( stat = "identity", fill= "green" )+
  labs( title = "Traveling Abroad", caption = "Kaggle Analysis By Fahd",
        x = "Travelled Abroad",
        y = "Travel Insurance")+
  theme_bw()+
  theme(plot.title = element_text(size = 23, hjust =  0.5),
        axis.title.x = element_text(size = 18, colour = "grey"),
        axis.title.y =  element_text(size = 18, color =  "Black"),
        axis.text.y =   element_text(size = 13, colour = "black"),
        axis.text.x =    element_text(size = 13, colour = "black"))
```

#Suggestions

Based off the above findings, some solutions to advertise travel insurance to age group, big families, non frequent flayers and people who have not traveled internationally are

- Advertise travel insurance when picking the flights domestically and internationally , and highlight all the advantages

- Put savings of purchasing travel insurance when displaying options so families  can see how much they are saving.

- put detailed information of what is included with travel insurance for the non frequent flyers so they understand what the importance

-Reinforce travel insurance from the beginning to the end of  transaction to show importance.






```{r}
TI <- Travel_Insurance %>%
  select( TravelInsurance)%>%
  filter(TravelInsurance == "1") %>% 
  summarise(TravelInsurance =n()) %>% 
  rename("PresentCount" = "TravelInsurance")
TI

```


```{r}
TA <-nrow(Travel_Insurance)
TA

```

```{r}
total = do.call(rbind, Map(data.frame, TI = TI, TA =TA))
total
```

```{r}
total %>% mutate( PercentagCount = TI/TA*100)
```

